A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2016-12-20 imaging_demo/ms.tex
Modify figures 1 and A1
From b76b8b9 (mnras):
====================

(*) Modify figures 1 and A1

In ms.tex,

(*) Minor changes in text

{\bf Heterogeneity in antenna arrays occurs primarily in two scenarios. The first is when the array is intended to be identical but differences in aperture and electrical properties arise due to deviations during the manufacturing process or from random deviant behaviour such as in dipoles of a phased array. The second scenario is when the array is designed to be heterogeneous to gain specific advantages such as sampling a wider range of spatial frequencies and decoupling the sky brightness distribution from the antenna power pattern. This has motivated a number of heterogeneous arrays such as the Combined Array for Research in Millimeter-wave Astronomy (CARMA; \citealt{woo04,wri10}), the Atacama Large Millimeter/submillimeter Array (ALMA; \citealt{igu09}), and the Very Long Baseline Array (VLBA). In practice, almost all arrays are heterogeneous albeit by varying degrees. The following analysis applies to both of the aforementioned scenarios although for purposes of clear demonstration, we will choose an example that is closer to the second scenario.}

@@

{\bf In the above example, we chose a scenario wherein the antennas in the array have large differences between them to clearly demonstrate the functionality in EPIC to image data from heterogeneous arrays. The analysis, however, is applicable to any heterogeneous array. In cases where the differences are smaller, the fidelity with which the sky model is recovered will still be degraded, although to a correspondingly smaller extent. To robustly quantify this degradation as a function of deviation from homogeneity will require image deconvolution and will be investigated in the future as it is currently beyond the scope of this paper.}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure11}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated.eps}
  \caption{Current and planned instruments in parameter space of
    number of complex multiplies and adds with MOFF and FX. The solid line
    is the boundary at which the number of operations with MOFF and 
    visibility-based imaging are equal. MOFF imaging is more efficient for 
    telescopes occupying the left of this line and vice versa. CHIME, HIRAX, 
    SKA1-LC, SKA1-LCD and all the HERA layouts except HERA-19 and HERA-37 lie 
    in the parameter space favoured by MOFF imaging. The dashed line shows the 
    projected trajectory of hypothetical expanded HERA layouts. The dotted line 
    similarly shows hypothetical expanded MWA layouts with more tiles added in 
    the same core. The gray shaded area denotes the projected trajectory of the 
    LWA bounded by LWA1 (left edge), LWA-OV (right edge), current layout 
    (bottom) and a four-fold increase in the number of elements within a 50 per 
    cent increase in the core size (top). Current instruments such as MWA and 
    LOFAR fall in a region favoured by visibility-based imaging.}
  \label{fig:parameter-space-computations-instruments}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure12}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended_v2}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended_v2.eps}
  \caption{Current and planned instruments in parameter space of baseline length and number of antennas with MOFF and FX. Lines of different colors denote different classes of antenna sizes (cyan - 1~m$^2$, blue - 7~m$^2$, purple - 16~m$^2$, green - 28~m$^2$, orange - 150~m$^2$, red - 740~m$^2$, gray - 5900~m$^2$). Lines of each color denote the boundary to the left of which MOFF algorithm is favoured for the corresponding antenna size. These lines shift rightward with increasing antenna size. The different antennas are color coded by roughly the class of antenna size they fall into. Thus symbols of one color falling to the left of a line of the same color indicate MOFF imaging is advantageous for those telescopes and vice versa. For example, MOFF imaging is favoured in HERA-331 and HERA-6769 because they lie to the left of the orange line but not so in cases of HERA-19 and HERA-37.}
  \label{fig:parameter-space-bll-nant-instruments}
\end{figure}

>>>>

{\bf Heterogeneity in antenna arrays occurs primarily in two scenarios. The first is when the array is intended to be identical but differences in aperture and electrical properties arise due to deviations during the manufacturing process or from random deviant behaviour such as differences in gains between dipoles in a phased array. In practice, due to this reason almost all arrays are heterogeneous albeit by varying degrees. The second scenario is when the array is designed to be heterogeneous to gain specific advantages such as sampling a wider range of spatial frequencies and decoupling the sky brightness distribution from the antenna power pattern. This has motivated a number of heterogeneous arrays such as the Combined Array for Research in Millimeter-wave Astronomy (CARMA; \citealt{woo04,wri10}), the Atacama Large Millimeter/submillimeter Array (ALMA; \citealt{igu09}), and the Very Long Baseline Array (VLBA). The following analysis applies to both of the aforementioned scenarios although for purposes of clear demonstration, we will choose an example with large differences across antennas, making it closer to the second scenario.}

@@

% {\bf In the above example, we chose a scenario wherein the antennas in the array have large differences between them to clearly demonstrate the functionality in EPIC to image data from heterogeneous arrays. The analysis, however, is applicable to any heterogeneous array. In cases where the differences are smaller, the fidelity with which the sky model is recovered will still be degraded, although to a correspondingly smaller extent. To robustly quantify this degradation as a function of deviation from homogeneity will require image deconvolution and will be investigated in the future as it is currently beyond the scope of this paper.}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure11}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated.eps}
  \caption{Current and planned instruments in parameter space of
    number of complex {\bf multiplications and additions}. The solid line
    is the boundary at which the number of operations with MOFF and 
    visibility-based imaging are equal. MOFF imaging is more efficient for 
    telescopes occupying the left of this line and vice versa. CHIME, HIRAX, 
    SKA1-LC, SKA1-LCD and all the HERA layouts except HERA-19 and HERA-37 lie 
    in the parameter space favoured by MOFF imaging. The dashed line shows the 
    projected trajectory of hypothetical expanded HERA layouts. The dotted line 
    similarly shows hypothetical expanded MWA layouts with more tiles added in 
    the same core. The gray shaded area denotes the projected trajectory of the 
    LWA bounded by LWA1 (left edge), LWA-OV (right edge), current layout 
    (bottom) and a four-fold increase in the number of elements within a 50 per 
    cent increase in the core size (top). Current instruments such as MWA and 
    LOFAR fall in a region favoured by visibility-based imaging.}
  \label{fig:parameter-space-computations-instruments}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure12}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended_v2}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended_v2.eps}
  \caption{Current and planned instruments in parameter space of baseline length and number of antennas. Lines of different colors denote different classes of antenna sizes (cyan - 1~m$^2$, blue - 7~m$^2$, purple - 16~m$^2$, green - 28~m$^2$, orange - 150~m$^2$, red - 740~m$^2$, gray - 5900~m$^2$). Lines of each color denote the boundary to the left of which MOFF algorithm is favoured for the corresponding antenna size. These lines shift rightward with increasing antenna size. The different antennas are color coded by roughly the class of antenna size they fall into. Thus symbols of one color falling to the left of a line of the same color indicate MOFF imaging is advantageous for those telescopes and vice versa. For example, MOFF imaging is favoured in HERA-331 and HERA-6769 because they lie to the left of the orange line but not so in cases of HERA-19 and HERA-37.}
  \label{fig:parameter-space-bll-nant-instruments}
\end{figure}
